Attempting to predict Heart Disease using a classical decision tree machine learning method

### 2022-11-15 Manuscript/paper.tex
added title and some notes for grader/prof in abstract

\title{Stats Paper}
\author{Olivia Frillici\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle
\begin{abstract}
    Here is the abstract.  
    \end{abstract}

>>>>

\title{Attempting to predict Heart Disease using a classical decision tree machine learning method }
\author{Olivia Frillici\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle
\begin{abstract}
    Here is the abstract. 
    SOME NOTES: I do not have my abstract or introduction written yet. Also I am aware of the lack of references and pictures, for the first draft really wanted to focus on the writing and attempting to get all of the coding done. 
    \end{abstract}
